Is Information Ontological or Physical, or Is It Perhaps Something Else? Some Remarks on Krzanowski's Approach to the Concept of Information

### 2023-02-01 ART_Mscislawski/Mscislaw.tex
Mscislawski article added

\begin{document}
\title{Is Information Ontological or Physical, or Is It Perhaps Something Else? Some Remarks on Krzanowski's Approach to the Concept of Information}
\maketitle

Łukasz Mścisławski

Politechnika Wrocławska

\url{https://orcid.org/0000-0003-0195-906}

\section{Abstract}
As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
 proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
\parencite[][]{ellis_space_2012}. %
 This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.

@@

The first distinction we would like to introduce, because we consider it important, is the distinction between two perspectives for the notion of information:

\begin{enumerate}
\item Ontological; and
\item Epistemological.
\end{enumerate}
These two areas of research are by no means mutually exclusive, but they pose slightly different kinds of questions. Krzanowski
%\label{ref:RNDf3GlACHwY4}(2020c, pp.37–38; 2022, pp.123–151)
\parencites*[][pp.37–38]{krzanowski_why_2020}[][pp.123–151]{krzanowski_ontological_2022} %
 presented an analogous distinction.\footnote{A~slightly different version is also presented in 
%\label{ref:RNDU9el6H16Mu}(Krzanowski, 2020b),
\parencite[][]{krzanowski_what_2020}, %
 where a~distinction between abstract and concrete information is introduced. There is a~little more on this subject below.} \textcolor{black}{For the purposes of this paper, however, they can be characterized as follows: The }\textit{\textcolor{black}{ontological}}\textcolor{black}{ (A) perspective mainly poses questions about what something is, how it exists, what its inherent properties are, and so on. It is worth noting here that within this research area, it is possible to pose a~question about the general structure of reality (i.e., its ontology and the ``location'' of information within it) and thus its ontological status. Such a~general perspective makes it possible to regard information as something tangible, so there is no need to reify it, although we cannot exclude such a~possibility. This perspective is of particular interest to Krzanowski and therefore also to this paper.}\footnotetext{As a~rule in this paper, ontology is not understood as a~network of concepts and relations between them, as is the case in some formal disciplines.}

@@

The second distinction that naturally arises when considering the notion of information relates to two approaches:

\begin{enumerate}
\item Qualitative; and
\item Quantitative.
\end{enumerate}
It is plain to see that these two approaches can be combined with the above perspectives. We could say that the epistemological perspective (B) is compatible with both approaches (I and II). Similarly, it is clear that perspective A~must be compatible with approach I. Nevertheless, some interesting issues arise:

@@

\section{The Concept of Physical Information}
``So Professor Isham, what is a~thing?''

@@

(I, science, Winter 2005, p. 20)

@@

The concept of \textit{abstract information} (IA) relates to some kind of cognitive activity, and based on Krzanowski's work, its main features can be expressed as follows
%\label{ref:RNDUbSu6SVSZt}(cf. Krzanowski, 2020b)
\parencite[cf.][]{krzanowski_what_2020} %
 :

IA1) It is some cognitive agent's interpretation of physical stimuli, which may be a~signal, the state of physical system, or some other physical phenomenon.

IA2) It exists for a~cognitive agent, or it is at least relative to some agent, so it is agent-relative or ontologically subjective.

IA3) It has meaning for a~cognitive agent.

IA4) The notion of a~cognitive agent is understood here in a~very broad sense, such that it may be human, another biological system, or some artificially intelligent system.

IA5) The existence of IA indicates the presence of an abstract notion somewhere outside of space and time.

@@

Nevertheless, Krzanowski's concept of \textit{physical information} refers to the concept of information using the term \textit{concrete information} (IC). He refers to an extensive list of authors whose views converge in this respect
%\label{ref:RND0gu0V9TSmq}(e.g. Turek, 1978; von Weizsäcker, 1982; Nagel, 2012; Dodig-Crnkovic, 2013; Heller, 2014; Rovelli, 2016; Wilczek, 2016; Davies, 2020),
\parencites[e.g.,][]{turek_filozoficzne_1978}[von][]{von_weizsacker_einheit_1982}[][]{nagel_mind_2012}[][]{dodig-crnkovic_alan_2013}[][]{heller_elementy_2014}[][]{rovelli_meaning_2016}[][]{wilczek_beautiful_2016}[][]{davies_demon_2020}, %
 to name but a~few). He also seems to be guided by an opposition to attributing only the features of IA to information in general 
%\label{ref:RNDE2Cvw6yFhp}(cf. Krzanowski, 2020a; 2020c).
\parencites[cf.][]{krzanowski_does_2020}[][]{krzanowski_why_2020}. %
 This triggers a~need to introduce a~different approach to the concept of information, a~more qualitative one (IC). Thus, the fundamental features of IC can be described as follows 
%\label{ref:RND57FEnOikEz}(cf. Krzanowski, 2020b, p.2):
\parencite[cf.][p.2]{krzanowski_what_2020}:%

IC0) IC exists in space and time (i.e., spacetime) as a~physical object, which is why it is called \textit{concrete}.

IC1) With reference to IC0, IC is a~physical phenomenon, so it exists objectively and is not relative to anything.

IC2) IC has no intrinsic meaning.

IC3) IC is, in a~sense, responsible for the organization of the physical world.

IC4) IC's existence implies existence in the physical world, somewhere in the space-time continuum.

@@

The presentation of the third feature is very, possibly even hopelessly, difficult. As Krzanowski emphasizes, any discussion of the concept of information becomes interwoven with notions such as \textit{form}, \textit{structure}, \textit{object}, and so on. Another fundamental problem here emerges when one tries to understand what it means for \textit{information} to be \textit{associated} with concepts like form and structure. To some extent, however, we can say that IC is in some way responsible for the organization of matter. This statement needs clarification, which Krzanowski provides by addressing the question of whether IC can be considered a~physical phenomenon
%\label{ref:RNDPU4TwRqmMg}(cf. Krzanowski, 2020b, pp.3–4).
\parencite[cf.][pp.3–4]{krzanowski_what_2020}. %
 More specifically, he describes \textit{physical information} binding with physical reality and mathematics (or mathematical structures) as follows:

PhI1) Physical information, as an inheritor of concrete information, is described as a~physical phenomenon. It should be highlighted that Krzanowski gives a~very special meaning to this statement, because physical information being a~physical phenomenon implies that this special type of information is an irreducible aspect of physical reality. In a~way, it recognizes something—whether it be the form, structure, or organization of some entity—as a~purely physical phenomenon in itself.

PhI2) Physical information exhibits properties that can be attributed to physical entities, namely that it:

PhI2a) is observable;

PhI2b) is ontologically objective;

PhI2c) can be manipulated;

PhI2d) has no intrinsic meaning; and

PhI2e) can be quantified or measured.

PhI3) Physical information is not a~mathematical or physical structure, thus preventing it from being considered as part of the realm of mathematical or physical structures, something that could easily lead to referring to such structures rather than to the (physical) information itself. However, where physical reality exists, there must also exist physical information
%\label{ref:RNDHah1cfOcK0}(cf. Krzanowski, 2020b, pp.3–4, 6).
\parencite[cf.][pp.3–4]{krzanowski_what_2020}.%

@@

\section{Remarks and Potential Avenues for Further Development}

@@

\textbf{R1}: Our first remark refers to the feature PhI3 and the possible relations that \textit{physical information} has with physical and mathematical structures. Krzanowski claims that where physical reality exists, there is physical information, and this suggests two possibilities:

a) Physical information is something inherent in matter, but this solution excludes any further discussion of the laws of physics, the possibility of cognizing physical reality, and so on.\footnote{We dare to posit that such a~solution is unsatisfying and of little interest. However, it still leaves us with unanswered questions: What is matter? Why is it formed in the way it is?}

b) Physical information is s\textit{omehow different from physical reality}, which is the research domain of physicists. Nevertheless, it is \textit{somehow} \textit{associated with} \textit{it}, albeit with a~different ontological status. It reveals itself through the existence of physical structures and the opportunity to cognize physical reality, even with measurement. Thus, we regard this as a~strong case for regarding it as a~\textit{meta-physical} reality, one that is tangible because it is ``responsible for'' creating physical structures. This last claim in some way justifies thinking of physical information as something \textit{inherent} to any physical object or phenomenon as an ``internal'' (meta-physical) constituent of it. Additionally, belonging to the ontological level and existing prior to any cognitive agent, physical information turns out to be more fundamental than any quantitative definition of information, albeit with the caveat contained in R2.

\textbf{R2}: It seems to us that PhI3 suggests that, in some way, the concept of physical information is not to be regarded as a~concrete mathematical structure. We would like to point out that this feature of the discussed concept needs further development. We claim that at the moment, the concept of physical information and its relations strongly depend upon what ontological assumptions are made, such as what is assumed to exist, whether there is any kind of metaphysical pluralism, and how particular types of entities (or structures) interrelate. For example, if a~kind of Platonic ontological structure of reality is assumed,\footnote{A~good example of such a~structure of reality was described by Penrose
%\label{ref:RNDHobtHTUq2h}(2006, pp.18–19).
\parencite*[][pp.18–19]{penrose_road_2006}.%
} it could also be assumed that a~part of the objectively existing Platonic mathematical world completely models (or causally acts upon and determines) physical reality, so physical structures are merely a~material representation of particular mathematical structures. In such a~case, physical information would surely be associated with certain mathematical structures, and this could be considered within any quantitative approach. There are of course easy way to escape this difficulty. More specifically, it suffices to assume that the mathematical structures of a~Platonic world do not describe the entirety of physical reality.\footnote{Such an example was also described by Penrose 
%\label{ref:RND0ROIWr74V2}(2006, pp.19–21).
\parencite*[][pp.19–21]{penrose_road_2006}.%
}

\textbf{R3}: Because physical information in some way inherits the features of concrete information, there is some difficulty with IC0, IC4, and PhI1. All these features suggest that physical information is ``located'' on the Newtonian-like stage of space and time. However, it seems that as Krzanowski describes it, space and time (or spacetime) are independent of physical information. General Relativity, however, describes spacetime (or space and time) as part of physical reality. Hence, this strongly suggests that we should regard physical information as something that is also in some way associated with the structure of spacetime. In other words, it ``contains information'' for spacetime. This aspect of the concept proposed by Krzanowski gives further backing for regarding physical information as something meta-physical while still being strictly connected to, or associated with, the physical level of the organization of matter.

\textbf{R4}: In all the key works
%\label{ref:RNDQIgL3jHQ2h}(i.e. Krzanowski, 2020b; 2020c; 2022),
\parencites[i.e.,][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022}, %
 there is a~lack of any linkage to quantum theories (e.g. quantum mechanics, quantum field theory, etc.). There is also no remark about no-go theorems (e.g. Kochen-Specker theorem), contextuality, and so on. These omissions are a~little bit puzzling, but they could be explained in two ways:

1) The concept of physical information refers to the very physical reality (cf. IC3 and PhI1), and as such, it also refers to the strange quantum realm. There is therefore no need to confer a~special status to this realm or any issues connected with the strange quantum features of it.

2) As with all physical theories, quantum theories are not ultimate theories but rather something through which we try to describe and explain physical reality. In this respect, it is a~purely epistemological perspective, while the subject of interest (the concept of physical information) adopts an ontological perspective. However, in this case, a~question arises as to whether any suggestions from philosophical research into quantum theories should be considered when exploring the concept of information, particularly for physical information. This matter requires extreme caution, however, because scientific theories tend to evolve relatively quickly, so drawing any far-reaching ontological conclusions from them is a~difficult undertaking. We therefore regard this issue as an open question.

\textbf{R5}: By virtue of IC3 and PhI1, the concept of physical information refers to physical reality, but it is not clear whether it is associated with the entirety of physical reality or just particular structures. In the latter case, a~question naturally arises about the relations in which particular ``physical information'' is associated with particular structures. On the other hand, it is precisely this reference to physical reality that allows the concept under discussion to be open to being ``contained'' in concepts of information, meaning higher levels of organisation of matter, such as chemical, biological, and so on. This opens up a~very interesting research area that relates to the possible types of information, their mutual relationships, and particularly the complexity (highly complex, non-linear, and chaotic systems) of it all. Indeed, Krzanowski
%\label{ref:RND0P5ufCGsH6}(2020b, p.13)
\parencite*[][p.13]{krzanowski_what_2020} %
 recognizes these areas. Another interesting question refers to potential relations with issues connected with computer science and natural computation. It again seems by virtue of the fact that physical information refers to physical reality, it could be included in such analyses. This problem is partially addressed by Krzanowski 
%\label{ref:RNDEEWlvPjTy4}(2022),
\parencite*[][]{krzanowski_ontological_2022}, %
 but we believe that it warrants further research, especially within the context of computations and relations between physical structures, some of which are very special, such as computing devices\footnote{By computing devices, we refer to artificial computing devices like personal computers, while we assume that any natural process can be regarded as a~form of computation, so any ``natural computing'' device is a~natural process.} and mathematical structures.

\textbf{R6}: If physical information is to be regarded as something that refers to structures in nature
%\label{ref:RND0usaVffGie}(Krzanowski, 2022, pp.86, 91–92),
\parencite[][pp.86]{krzanowski_ontological_2022}, %
 we should also account for the following issues:

a) Physical structures are dynamic, so we should try to answer the following question: Are changes in physical structures really also changing the physical information, so it should be regarded as dynamic. Or does physical information contain the ``dynamics'' of these physical structures? Is it perhaps rather the case that changes in physical reality, caused naturally or otherwise, take place in a~manner that is determined by physical information?

b) Perhaps it is a~good idea to regard physical information as something ``standing behind'' physical structures and their dynamics (changes). One possibility would be to view physical information as a~kind of potentiality for creating (physical) structures.\footnote{From private correspondence with R. Krzanowski.} This could be based on the fairly obvious observation that structures exist in nature, and nature tends to create structures, yet the idea needs further research, because the potential to create structures does not necessarily stem from the fact that there has to be structures.\footnote{It should be noted that this issue was addressed by Czesław Białobrzeski, among others. To explain how it is possible for structures to arise in nature, Białobrzeski adapted the ontological ideas of Nicolai Hartmann and introduced the category of organisation (Polish: \textit{kategoria ustrojowości}), which is responsible for allowing higher layers of reality to arise, as well as a~real factor that he called potentiality that is responsible for the state and organisation of a~system
%\label{ref:RNDzTObVw8edO}(cf. Białobrzeski, 1984, pp.243–247; Mścisławski, 2017).
\parencites[cf.][pp.243–247]{bialobrzeski_podstawy_1984}[][]{mscislawski_miedzy_2017}. %
 This area of research is closely connected to the issue of the relation between physical information and complexity (see R5 above).}

c) It seems that physical information, by virtue of being ``responsible'' for manifesting physical structures, makes it possible for epistemic concepts of information to exist.

\textbf{R7}: A~subtle issue arises when we question the ontological status of physical information, as well as its genesis. Indeed, there are many opportunities for further research in this area
%\label{ref:RNDHDALPOZtBU}(cf. Krzanowski, 2020b, p.13).
\parencite[cf.][p.13]{krzanowski_what_2020}. %
 There is also a~very important question about the causal relations between physical information and the physical reality with which it is connected. Within this context, the problematic relations between matter, physical information, and the laws of physics arise once more 
%\label{ref:RNDtQjmz6zqlx}(e.g. Davies, 2007).
\parencite[e.g.,][]{davies_implications_2007}.%

@@

\section{Acknowledgements}
We would like to express our gratitude to the two anonymous reviewers for their careful reading of our manuscript and extremely valuable and helpful comments.

\section{Bibliography}
Adriaans, P. and Benthem, J. van, 2008. \textit{Philosophy of information}. Amsterdam, The Netherlands; Boston: North Holland.

Białobrzeski, C., 1984. Podstawy poznawcze fizyki świata atomowego. In: \textit{Podstawy poznawcze fizyki świata atomowego}, Wyd. 2 rozszerzone. Warszawa: Państwowe Wydawnictwo Naukowe. pp.19–288.

Burgin, M., 2010. \textit{Theory of information: fundamentality, diversity and unification}. World Scientific series in information studies. Hackensack, NJ: World Scientific Pub Co Inc.

>>>>

\begin{artengenv}{Łukasz Mścisławski}
	{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
	{Is information ontological or physical, or is it perhaps something else?\ldots}
	{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
	{Wrocław University of Science and Technology}
	{As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
	%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
	\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
	 proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
	%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
	\parencite[][]{ellis_space_2012}. %
	 This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.
	}
	{physical information, ontology, physics, philosophy of information.}

%\begin{document}
%\title{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
%\maketitle
%
%Łukasz Mścisławski
%
%Politechnika Wrocławska
%
%\url{https://orcid.org/0000-0003-0195-906}
%
%\section{Abstract}
%As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
%%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
%\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
% proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
%%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
%\parencite[][]{ellis_space_2012}. %
% This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.

@@

The first distinction we would like to introduce, because we consider it important, is the distinction between two perspectives for the notion of information:
\begin{enumerate}[label=(\Alph*)]
\item Ontological; and
\item Epistemological.
\end{enumerate}
These two areas of research are by no means mutually exclusive, but they pose slightly different kinds of questions. Krzanowski
%\label{ref:RNDf3GlACHwY4}(2020c, pp.37–38; 2022, pp.123–151)
\parencites*[][pp.37–38]{krzanowski_why_2020}[][pp.123–151]{krzanowski_ontological_2022} %
 presented an analogous distinction.\footnote{A~slightly different version is also presented in 
%\label{ref:RNDU9el6H16Mu}(Krzanowski, 2020b),
\parencite[][]{krzanowski_what_2020}, %
 where a~distinction between abstract and concrete information is introduced. There is a~little more on this subject below.}
 For the purposes of this paper, however, they can be characterized as follows: The \textit{ontological} (A) perspective mainly poses questions about what something is, how it exists, what its inherent properties are, and so on. It is worth noting here that within this research area, it is possible to pose a~question about the general structure of reality (i.e., its ontology and the ``location'' of information within it) and thus its ontological status. Such a~general perspective makes it possible to regard information as something tangible, so there is no need to reify it, although we cannot exclude such a~possibility. This perspective is of particular interest to Krzanowski and therefore also to this paper.\footnotetext{As a~rule in this paper, ontology is not understood as a~network of concepts and relations between them, as is the case in some formal disciplines.}

@@

The second distinction that naturally arises when considering the notion of information relates to two approaches:
\begin{enumerate}[label=(\Roman*)]
\item Qualitative; and
\item Quantitative.
\end{enumerate}
It is plain to see that these two approaches can be combined with the above perspectives. We could say that the epistemological perspective (B) is compatible with both approaches (I and II). Similarly, it is clear that perspective A~must be compatible with approach I. Nevertheless, some interesting issues arise:

@@

\section{The concept of physical information}

\begin{flushright}
\begin{footnotesize}
\vskip -1\baselineskip
``So Professor Isham, what is a~thing?''

@@

\vskip -.4\baselineskip
\parencite{medeiros_2005}
\end{footnotesize}
\end{flushright}
%(I, science, Winter 2005, p. 20)
%\vskip 2\baselineskip

@@

The concept of \textit{abstract information} (IA) relates to some kind of cognitive activity, and based on Krzanowski's work, its main features can be expressed as follows
%\label{ref:RNDUbSu6SVSZt}(cf. Krzanowski, 2020b)
\parencite[cf.][]{krzanowski_what_2020}: %
\begin{enumerate}[label=(IA\arabic*)]
\item It is some cognitive agent's interpretation of physical stimuli, which may be a~signal, the state of physical system, or some other physical phenomenon.
\item It exists for a~cognitive agent, or it is at least relative to some agent, so it is agent-relative or ontologically subjective.
\item It has meaning for a~cognitive agent.
\item The notion of a~cognitive agent is understood here in a~very broad sense, such that it may be human, another biological system, or some artificially intelligent system.
\item The existence of IA indicates the presence of an abstract notion somewhere outside of space and time.
\end{enumerate}

@@

Nevertheless, Krzanowski's concept of \textit{physical information} refers to the concept of information using the term \textit{concrete information} (IC). He refers to an extensive list of authors whose views converge in this respect
%\label{ref:RND0gu0V9TSmq}(e.g. Turek, 1978; von Weizsäcker, 1982; Nagel, 2012; Dodig-Crnkovic, 2013; Heller, 2014; Rovelli, 2016; Wilczek, 2016; Davies, 2020),
\parencites[e.g.,][]{turek_filozoficzne_1978}[von][]{von_weizsacker_einheit_1982}[][]{nagel_mind_2012}[][]{dodig-crnkovic_alan_2013}[][]{heller_elementy_2014}[][]{rovelli_meaning_2016}[][]{wilczek_beautiful_2016}[][]{davies_demon_2020}, %
 to name but a~few). He also seems to be guided by an opposition to attributing only the features of IA to information in general 
%\label{ref:RNDE2Cvw6yFhp}(cf. Krzanowski, 2020a; 2020c).
\parencites[cf.][]{krzanowski_does_2020}[][]{krzanowski_why_2020}. %
 This triggers a~need to introduce a~different approach to the concept of information, a~more qualitative one (IC). Thus, the fundamental features of IC can be described as follows 
%\label{ref:RND57FEnOikEz}(cf. Krzanowski, 2020b, p.2):
\parencite[cf.][p.2]{krzanowski_what_2020}:%
\begin{enumerate}[label=(IC\arabic*), start=0]
\item IC exists in space and time (i.e., spacetime) as a~physical object, which is why it is called \textit{concrete}.
\item With reference to IC0, IC is a~physical phenomenon, so it exists objectively and is not relative to anything.
\item IC has no intrinsic meaning.
\item IC is, in a~sense, responsible for the organization of the physical world.
\item IC's existence implies existence in the physical world, somewhere in the space-time continuum.
\end{enumerate}

@@

The presentation of the third feature is very, possibly even hopelessly, difficult. As Krzanowski emphasizes, any discussion of the concept of information becomes interwoven with notions such as \textit{form}, \textit{structure}, \textit{object}, and so on. Another fundamental problem here emerges when one tries to understand what it means for \textit{information} to be \textit{associated} with concepts like form and structure. To some extent, however, we can say that IC is in some way responsible for the organization of matter. This statement needs clarification, which Krzanowski provides by addressing the question of whether IC can be considered a~physical phenomenon
%\label{ref:RNDPU4TwRqmMg}(cf. Krzanowski, 2020b, pp.3–4).
\parencite[cf.][pp.3–4]{krzanowski_what_2020}. %
 More specifically, he describes \textit{physical information} binding with physical reality and mathematics (or mathematical structures) as follows:
 \newlist{mscislaw}{enumerate}{2}
 \setlist[mscislaw,1]{label=(PhI\arabic*)}
 \setlist[mscislaw,2]{label=(PhI\arabic{mscislawi}.\alph*)}
\begin{mscislaw}
\item  Physical information, as an inheritor of concrete information, is described as a~physical phenomenon. It should be highlighted that Krzanowski gives a~very special meaning to this statement, because physical information being a~physical phenomenon implies that this special type of information is an irreducible aspect of physical reality. In a~way, it recognizes something—whether it be the form, structure, or organization of some entity—as a~purely physical phenomenon in itself.

\item  Physical information exhibits properties that can be attributed to physical entities, namely that it:
\begin{mscislaw}
\item is observable;
\item is ontologically objective;
\item can be manipulated;
\item has no intrinsic meaning; and
\item can be quantified or measured.
\end{mscislaw}
\item  Physical information is not a~mathematical or physical structure, thus preventing it from being considered as part of the realm of mathematical or physical structures, something that could easily lead to referring to such structures rather than to the (physical) information itself. However, where physical reality exists, there must also exist physical information
%\label{ref:RNDHah1cfOcK0}(cf. Krzanowski, 2020b, pp.3–4, 6).
\parencite[cf.][pp.3–4]{krzanowski_what_2020}.%
\end{mscislaw}

@@

\section{Remarks and potential avenues for further development}

@@

\paragraph{R1:} Our first remark refers to the feature PhI3 and the possible relations that \textit{physical information} has with physical and mathematical structures. Krzanowski claims that where physical reality exists, there is physical information, and this suggests two possibilities:
\begin{enumerate}[label=(\alph*)]
\item Physical information is something inherent in matter, but this solution excludes any further discussion of the laws of physics, the possibility of cognizing physical reality, and so on.\footnote{We dare to posit that such a~solution is unsatisfying and of little interest. However, it still leaves us with unanswered questions: What is matter? Why is it formed in the way it is?}
\item Physical information is s\textit{omehow different from physical reality}, which is the research domain of physicists. Nevertheless, it is \textit{somehow} \textit{associated with} \textit{it}, albeit with a~different ontological status. It reveals itself through the existence of physical structures and the opportunity to cognize physical reality, even with measurement. Thus, we regard this as a~strong case for regarding it as a~\textit{meta-physical} reality, one that is tangible because it is ``responsible for'' creating physical structures. This last claim in some way justifies thinking of physical information as something \textit{inherent} to any physical object or phenomenon as an ``internal'' (meta-physical) constituent of it. Additionally, belonging to the ontological level and existing prior to any cognitive agent, physical information turns out to be more fundamental than any quantitative definition of information, albeit with the caveat contained in R2.
\end{enumerate}

\paragraph{R2:} It seems to us that PhI3 suggests that, in some way, the concept of physical information is not to be regarded as a~concrete mathematical structure. We would like to point out that this feature of the discussed concept needs further development. We claim that at the moment, the concept of physical information and its relations strongly depend upon what ontological assumptions are made, such as what is assumed to exist, whether there is any kind of metaphysical pluralism, and how particular types of entities (or structures) interrelate. For example, if a~kind of Platonic ontological structure of reality is assumed,\footnote{A~good example of such a~structure of reality was described by Penrose
%\label{ref:RNDHobtHTUq2h}(2006, pp.18–19).
\parencite*[][pp.18–19]{penrose_road_2006}.%
} it could also be assumed that a~part of the objectively existing Platonic mathematical world completely models (or causally acts upon and determines) physical reality, so physical structures are merely a~material representation of particular mathematical structures. In such a~case, physical information would surely be associated with certain mathematical structures, and this could be considered within any quantitative approach. There are of course easy way to escape this difficulty. More specifically, it suffices to assume that the mathematical structures of a~Platonic world do not describe the entirety of physical reality.\footnote{Such an example was also described by Penrose 
%\label{ref:RND0ROIWr74V2}(2006, pp.19–21).
\parencite*[][pp.19–21]{penrose_road_2006}.%
}

\paragraph{R3:} Because physical information in some way inherits the features of concrete information, there is some difficulty with IC0, IC4, and PhI1. All these features suggest that physical information is ``located'' on the Newtonian-like stage of space and time. However, it seems that as Krzanowski describes it, space and time (or spacetime) are independent of physical information. General Relativity, however, describes spacetime (or space and time) as part of physical reality. Hence, this strongly suggests that we should regard physical information as something that is also in some way associated with the structure of spacetime. In other words, it ``contains information'' for spacetime. This aspect of the concept proposed by Krzanowski gives further backing for regarding physical information as something meta-physical while still being strictly connected to, or associated with, the physical level of the organization of matter.

\paragraph{R4:} In all the key works
%\label{ref:RNDQIgL3jHQ2h}(i.e. Krzanowski, 2020b; 2020c; 2022),
\parencites[i.e.,][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022}, %
 there is a~lack of any linkage to quantum theories (e.g. quantum mechanics, quantum field theory, etc.). There is also no remark about no-go theorems (e.g. Kochen-Specker theorem), contextuality, and so on. These omissions are a~little bit puzzling, but they could be explained in two ways:
\begin{enumerate}[label=(\arabic*)]
\item The concept of physical information refers to the very physical reality (cf. IC3 and PhI1), and as such, it also refers to the strange quantum realm. There is therefore no need to confer a~special status to this realm or any issues connected with the strange quantum features of it.

\item As with all physical theories, quantum theories are not ultimate theories but rather something through which we try to describe and explain physical reality. In this respect, it is a~purely epistemological perspective, while the subject of interest (the concept of physical information) adopts an ontological perspective. However, in this case, a~question arises as to whether any suggestions from philosophical research into quantum theories should be considered when exploring the concept of information, particularly for physical information. This matter requires extreme caution, however, because scientific theories tend to evolve relatively quickly, so drawing any far-reaching ontological conclusions from them is a~difficult undertaking. We therefore regard this issue as an open question.
\end{enumerate}
\paragraph{R5:} By virtue of IC3 and PhI1, the concept of physical information refers to physical reality, but it is not clear whether it is associated with the entirety of physical reality or just particular structures. In the latter case, a~question naturally arises about the relations in which particular ``physical information'' is associated with particular structures. On the other hand, it is precisely this reference to physical reality that allows the concept under discussion to be open to being ``contained'' in concepts of information, meaning higher levels of organisation of matter, such as chemical, biological, and so on. This opens up a~very interesting research area that relates to the possible types of information, their mutual relationships, and particularly the complexity (highly complex, non-linear, and chaotic systems) of it all. Indeed, Krzanowski
%\label{ref:RND0P5ufCGsH6}(2020b, p.13)
\parencite*[][p.13]{krzanowski_what_2020} %
 recognizes these areas. Another interesting question refers to potential relations with issues connected with computer science and natural computation. It again seems by virtue of the fact that physical information refers to physical reality, it could be included in such analyses. This problem is partially addressed by Krzanowski 
%\label{ref:RNDEEWlvPjTy4}(2022),
\parencite*[][]{krzanowski_ontological_2022}, %
 but we believe that it warrants further research, especially within the context of computations and relations between physical structures, some of which are very special, such as computing devices\footnote{By computing devices, we refer to artificial computing devices like personal computers, while we assume that any natural process can be regarded as a~form of computation, so any ``natural computing'' device is a~natural process.} and mathematical structures.

\paragraph{R6:} If physical information is to be regarded as something that refers to structures in nature
%\label{ref:RND0usaVffGie}(Krzanowski, 2022, pp.86, 91–92),
\parencite[][pp.86]{krzanowski_ontological_2022}, %
 we should also account for the following issues:
\begin{enumerate}[label=(\alph*)]
\item Physical structures are dynamic, so we should try to answer the following question: Are changes in physical structures really also changing the physical information, so it should be regarded as dynamic. Or does physical information contain the ``dynamics'' of these physical structures? Is it perhaps rather the case that changes in physical reality, caused naturally or otherwise, take place in a~manner that is determined by physical information?
\item Perhaps it is a~good idea to regard physical information as something ``standing behind'' physical structures and their dynamics (changes). One possibility would be to view physical information as a~kind of potentiality for creating (physical) structures.\footnote{From private correspondence with R. Krzanowski.} This could be based on the fairly obvious observation that structures exist in nature, and nature tends to create structures, yet the idea needs further research, because the potential to create structures does not necessarily stem from the fact that there has to be structures.\footnote{It should be noted that this issue was addressed by Czesław Białobrzeski, among others. To explain how it is possible for structures to arise in nature, Białobrzeski adapted the ontological ideas of Nicolai Hartmann and introduced the category of organisation (Polish: \textit{kategoria ustrojowości}), which is responsible for allowing higher layers of reality to arise, as well as a~real factor that he called potentiality that is responsible for the state and organisation of a~system
%\label{ref:RNDzTObVw8edO}(cf. Białobrzeski, 1984, pp.243–247; Mścisławski, 2017).
\parencites[cf.][pp.243–247]{bialobrzeski_podstawy_1984}[][]{mscislawski_miedzy_2017}. %
 This area of research is closely connected to the issue of the relation between physical information and complexity (see R5 above).}

\item It seems that physical information, by virtue of being ``responsible'' for manifesting physical structures, makes it possible for epistemic concepts of information to exist.
\end{enumerate}
\paragraph{R7:} A~subtle issue arises when we question the ontological status of physical information, as well as its genesis. Indeed, there are many opportunities for further research in this area
%\label{ref:RNDHDALPOZtBU}(cf. Krzanowski, 2020b, p.13).
\parencite[cf.][p.13]{krzanowski_what_2020}. %
 There is also a~very important question about the causal relations between physical information and the physical reality with which it is connected. Within this context, the problematic relations between matter, physical information, and the laws of physics arise once more 
%\label{ref:RNDtQjmz6zqlx}(e.g. Davies, 2007).
\parencite[e.g.,][]{davies_implications_2007}.%

@@

\paragraph{Acknowledgements.}
We would like to express our gratitude to the two anonymous reviewers for their careful reading of our manuscript and extremely valuable and helpful comments.

\end{artengenv}

%\section{Bibliography}
%Adriaans, P. and Benthem, J. van, 2008. \textit{Philosophy of information}. Amsterdam, The Netherlands; Boston: North Holland.
%
%Białobrzeski, C., 1984. Podstawy poznawcze fizyki świata atomowego. In: \textit{Podstawy poznawcze fizyki świata atomowego}, Wyd. 2 rozszerzone. Warszawa: Państwowe Wydawnictwo Naukowe. pp.19–288.
%
%Burgin, M., 2010. \textit{Theory of information: fundamentality, diversity and unification}. World Scientific series in information studies. Hackensack, NJ: World Scientific Pub Co Inc.
%
